%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.0.1, 11 September 2016) written by
% LianTze Lim (liantze@gmail.com), based on the 
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper]{altacv}

\usepackage{hyperref}
\usepackage{fontspec}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=black,
}
 
\urlstyle{same}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you'll need to install
%% Academicons.ttf in your operating system's font %% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

% Change the font if you want to.
\setmainfont[Path = ./,  %% Optional; but UPDATE this if 
                         %% your font files are in a folder
 Extension = .otf,
 UprightFont = *-Regular,
 BoldFont = *-Bold,
 ItalicFont = *-Light
 ]
{Dosis}
% \fontspec{Dosis}

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkBrown}{HTML}{3F2A14}
\definecolor{Gold}{HTML}{FFD700}
\definecolor{Black}{HTML}{000000}
\definecolor{Green}{HTML}{009900}

%\colorlet{heading}{VividPurple}
\colorlet{heading}{DarkBrown}
\colorlet{heading-line}{Green}
\colorlet{accent}{DarkBrown}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{Black}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
% \addbibresource{sample.bib}

\begin{document}
\name{Ivan Trusov}
\tagline{Desired position: Senior Data Scientist}

\personalinfo{
  \email{\href{mailto:renardeinside@gmail.com}{renardeinside@gmail.com}}
  \homepage{\href{https://renardeinside.github.io}{renardeinside.github.io}}
  \github{\href{https://github.com/renardeinside}{renardeinside}}
%   \kaggle{\href{https://www.kaggle.com/renardeinside}{renardeinside}}
}

%% Make the header extend all the way to the right, if you want. Extend the right margin by 8cm (=6.8cm marginparwidth + 1.2cm marginparsep)
\begin{adjustwidth}{}{-8cm}
\makecvheader
\end{adjustwidth}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}

\cveventnew{Senior Data Scientist}
    {Sberbank of Russia}
    {
        Developed from research to production usage more than 5 models for probability of default and segment classification (with Apache Spark and Python).\linebreak
        Implemented model monitoring system using non-parametric statistical tests on models features and predictions. 
    }
    {April 2017 -- Ongoing}
{}

\divider

\cveventnew{Middle Data Engineer}
    {Sberbank of Russia}
    {
        Implemented various ETL algorithms for different analytical requests. \linebreak
        Integrated CDH cluster with IPA for Kerberos security and production-ready user access solution.
    }
    {September 2016 -- April 2017}
{}

\divider

\cveventnew{Middle Data Scientist}
    {MobileTeleSystems (MTS)}
    {
        Created prediction models for target marketing in Apache Spark and Python. \linebreak
        Implemented various geolocation algorithms in Teradata SQL. \linebreak
        Created streaming data pipeline for CDR parsing in Spark Streaming. \linebreak
    }
    {December 2015 -- September 2016}
{}

\divider

\cveventnew{Junior Data Scientist}
    {Veon Russia}
    {
        Created models for churn prediction, tariff migration and device migration in Python. \linebreak
        Developed data pipeline in Apache Spark for loading historical datamarts from Oracle DB to Hive. \linebreak
        Implemented discount optimization algorithm with Apache Spark in Scala.
    }
    {December 2014 -- December 2015}
{}

\divider

\cveventnew{Junior Data Scientist}
    {MobileTeleSystems (MTS)}
    {
    Developed in Python web scraping data pipeline for MNP process. \linebreak
    Developed optimization algorithm for A/B split, based on the Kolmogorov-Smirnov test acceptance of samples. 
    }
    {March 2014 -- December 2014} 
{}

% Introduce, Implement, 
% add diploma themes
% Experience -> Employment 
% Add lectures experience 
% Add skills section with languages 
% Add objective (or a position) which i want to get 
% Add achievements & interests section 
% Add Personal statements 
% Move in X to the end of statements
% Add photo 

\clearpage


\end{document}
